\begin{frame}{Feedback policy and opportunities}

{\color{red} \scriptsize 
Receiving feedback requires your active participation. In red, I highlight what you need to do!}\\

\vspace{0.1cm}

{\bf The would be numerous opportunities to receive feedback}:

\begin{itemize}
{\small
  \item Verbal feedback in face-to-face or online (lectures, workshops)
  \begin{itemize}
  {\scriptsize
    \item {\color{red}Please try and speak up! In online Zoom sessions, raise your hand to speak (or just interrupt me), or use the Zoom chat.}
  }
  \end{itemize}

  \item Feedback on your workshop submissions
  \begin{itemize}
  {\scriptsize
    \item {\color{red}You can't receive feedback if you don't submit. Don't miss the deadlines!}
    \item {\color{red}The more of the formative assessment you complete, the more feedback you get.}\\
  }
  \end{itemize}
 
  \item Detailed model solutions and a marking scheme for each workshop
  \begin{itemize}
  {\scriptsize
    \item This is the ultimate workshop feedback!
    \item {\color{red}Study the published solutions, contrast with your own, and reflect.}
  }
  \end{itemize}
 
  \item Feedback during online sessions
  \begin{itemize}
  {\scriptsize 
    \item Common issues / misconceptions seen in workshops,
      will be addressed in lectures
  }
  \end{itemize}

  \item More personalised feedback on 1-on-1 meetings (face to face, or on Zoom)
  \begin{itemize}
  {\scriptsize
    \item {\color{red}On demand! Please come to my office or request an appointment.}
  }
  \end{itemize}
    
  \item Canvas discussion boards, e-mail.
  \begin{itemize}
  {\scriptsize
    \item {\color{red}Participate!}
  }
  \end{itemize}
  
}
\end{itemize} 
    
\end{frame}
